\textbf{Research:}

\href{https://www.wcu.edu/learn/departments-schools-colleges/cas/science-and-math/biology/biology-faculty-staff/heather-coan.aspx}{\ul{PI: Heather Coan, Western Carolina University.}} \hfill Spring 2016 -- Present \\
\indent Contact: \href{mailto:hacoan@email.wcu.edu}{hacoan@email.wcu.edu}
\setlist{nolistsep}
\begin{itemize}[noitemsep]
\item Examined the ability of keratin to modulate the autophagy pathway in human cells.
\item Maintained HEK-293 cultures for the lab group, and prepared cultures for experiments.
\item Optimized transfection into HEK cells of a dual-reporter autophagy biomarker plasmid.
\item Visualized changes in the autophagy pathway using wide-field epifluorescence microscopy.
\item Compiled and analyzed data using FIJI and \texttt{R}.
\end{itemize}

\href{https://www.wcu.edu/learn/departments-schools-colleges/cas/science-and-math/mathcsdept/mathematics-and-computer-science-faculty-and-staff/andrew-penland.aspx}{\ul{PI: Andrew Penland, Western Carolina University.}} \hfill Fall 2019 -- Present \\
\indent Contact: \href{mailto:adpenland@email.wcu.edu}{adpenland@email.wcu.edu}
\setlist{nolistsep}
\begin{itemize}[noitemsep]
\item Simulated results from an Armitage-Doll carcinogenesis model on a large scale. 
\item Graphically displayed results from large simulations.
\item Instructed research group members in using \texttt{R} and the tidyverse suite.
\item Helped solve problems related to probability distributions on hypergraphs.
\end{itemize}

\href{https://www.wcu.edu/learn/departments-schools-colleges/cas/science-and-math/mathcsdept/mathematics-and-computer-science-faculty-and-staff/jeff-lawson.aspx}{\ul{PI: Jeff Lawson, Western Carolina University.}} \hfill Fall 2019 -- Present \\
\indent Contact: \href{mailto:jlawson@email.wcu.edu}{jlawson@email.wcu.edu}
\setlist{nolistsep}
\begin{itemize}[noitemsep]
\item Analyzed least squares models for logistic growth ODE parameter recovery from time series data.
\item Developed a suite of functions for replicable time series data generation and least squares fitting in \texttt{R}.
\end{itemize}

\href{https://publichealth.uga.edu/faculty-member/andreas-handel/}{\ul{PI: Andreas Handel, University of Georgia.}} \hfill Summer 2019 \\
\indent Contact: \href{mailto:ahandel@uga.edu}{ahandel@uga.edu} \\
\indent Website: \href{https://www.andreashandel.com/}{https://www.andreashandel.com/}
\setlist{nolistsep}
\begin{itemize}[noitemsep]
\item Participant in the 2019 REU site Population Biology of Infectious Diseases at the University of Georgia, and was funded by the NIH.
\item Cleaned and joined a complex relational data set from a \href{https://www.jabfm.org/content/32/2/226}{\ul{2016--2017 study}} at the University of Georgia student health center.
\item Analyzed the impact of viral load estimates from qPCR data on clinical prognoses and treatment of influenza A. 
\item Modeled and visualized the relationships between several variables using \texttt{R}, and presented results using \texttt{R}-Markdown.
\end{itemize}

\href{https://biology.uncg.edu/people/louis-marie-bobay-2/}{\ul{PI: Louis-Marie Bobay, UNC Greensboro.}} \hfill Summer 2018 \\
\indent Contact: \href{mailto:ljbobay@uncg.edu}{ljbobay@uncg.edu} 
\setlist{nolistsep}
\begin{itemize}[noitemsep]
\item Participant in the 2018 REU site Math-Biology at the University of North Carolina at Greensboro, and was funded by the NSF.
\item Constructed a probabilistic model for determining the probability of $n$ number of convergent mutations between two bacterial genomes.
\item Verified the accuracy of the model using Monte-Carlo simulation methods in \texttt{Python}.
\item Visualized model predictions, effects of parameters, and simulation results in \texttt{R}.
\item I also worked extensively with Dr. Johnathan Rowell (contact: \href{mailto:jtrowell@uncg.edu}{jtrowell@uncg.edu}) on the same project.
\end{itemize}

\ul{OEIS (On-line Encyclopedia of Integer Sequences) Contributions} \\
\indent All of these sequences can be viewed at \url{https://oeis.org}.
\setlist{nolistsep}
\begin{itemize}[noitemsep]
\item Author of sequence \href{https://oeis.org/A319302}{\ul{A319302}}.
\item Author of sequence \href{https://oeis.org/A309092}{\ul{A309092}}.
\item Wrote Python code and generated a b-file for sequence \href{https://oeis.org/A110529}{\ul{A110529}.}
\end{itemize}