\documentclass[11pt]{article}

\usepackage{microtype}
\usepackage[margin=1in]{geometry}
\usepackage{hyperref}
\usepackage{soul}
\usepackage{setspace}
\usepackage{enumitem}
\usepackage{booktabs}
\usepackage{footnote}
\usepackage{multirow}

\usepackage[T1]{fontenc}
\usepackage{lmodern}

\onehalfspacing

\begin{document}

\begin{center}
\large{
	{\bf CURRICULUM VITAE} \\
	W. Zane Billings \\}
	\hrulefill
\end{center}

\normalsize

{\bf Contact Information:}
\setlist{nolistsep}
\begin{itemize}[noitemsep]
\item Email: \href{mailto:wesley.billings@uga.edu}{\texttt{wesley.billings@uga.edu}}
%\item Mobile: (980) 241-7815
\item Homepage: \url{https://wzbillings.com} (Connects to GitHub and LinkedIn)
\item Office address: 121 B.S. Miller Hall, 101 Buck Rd, Athens, GA 30607.
\end{itemize}

\vspace{0.2in}
\textbf{Education:}

\begin{itemize}
\item Current. PhD, Epidemiology and Biostatistics, University of Georgia.
\item 2020. B.S., Biology and Mathematics, Western Carolina University.
\end{itemize}

\vspace{0.2in}
\textbf{Awards:}

\begin{itemize}
    \item \textbf{Georgia Research Education Award Traineeship}, University of Georgia, awarded 2020. Full funding for doctoral degree for 5 years.
    \item Summer Institute in Statistics and Modeling in Infectious Diseases (SISMID) Scholarship, University of Washington, awarded Summer 2022.
    \item Doctoral Service Award, Department of Epidemiology \& Biostatistics, University of Georgia, awarded Spring 2022.
\end{itemize}

\vspace{0.2in}
\textbf{Publications:}

\setlist{nolistsep}
\begin{itemize}[noitemsep]
\item Mckay B, Ebell M, \ul{Billings WZ}, Dale AP, Shen Y, Handel A. Associations between relative viral load at diagnosis and influenza A symptoms and recovery. \textit{Open Forum Infectious Diseases}. 2020; 7(11).
\end{itemize}

\vspace{0.2in}
\textbf{Presentations:}

\setlist{nolistsep}
\begin{itemize}[noitemsep]
\item \ul{Billings WZ}, Handel A, et al. Longitudinal trajectories of influenza immune response after repeat vaccination. Talk presented at the CIVR-HRP annual meeting; May 2022; Athens, GA.
\item \ul{Billings WZ}, Handel A, et al. How do preexisting immunity and host factors interact to impact influenza vaccine response? Talk presented at the NIH CIVICs annual meeting; August 2021; virtual.
\item \ul{Billings WZ}, Handel A. Exploring the effect of host factors on the relationship between pre-existing immunity and influenza vaccine response. Poster presented at Ecology and Evolution of Infectious Diseases meeting; 2021; virtual.
\item \ul{Billings WZ}, Handel A. How does pre-existing immunity interact with other factors to impact influenza vaccine responses? Talk presented at the CIVR-HRP annual meeting; May 2021; virtual.
\end{itemize}

\vfill\newpage
\textbf{Teaching and mentoring:}

\ul{Undergraduate mentoring}
\begin{itemize}
    \item Primary mentor for one undergraduate student for the PopBio 2022 program, leading to an in-progress manuscript.
    \item Co-mentor for one undergraduate student for the PopBio 2021 program, leading to an in-progress manuscript.
\end{itemize}

\ul{Workshops}
\begin{itemize}
    \item Reproducible research with \texttt{R} and R Markdown, June 2022. Population Biology of Infectious Diseases REU program.
    \item \texttt{R} and SAS primer, August 2021. UGA College of Public Health.
    \item Data visualization using \texttt{ggplot2}, June 2021. Population Biology of Infectious Diseases REU program.
\end{itemize}

\ul{Teaching assistant} \hfill Fall 2022
\begin{itemize}
    \item TA for EPID 7500: Introduction to Coding in R, Data Science and Simulation for Public Health and the Life Sciences at the University of Georgia.
    \item Worked directly with students in writing and debugging R code during instructional time.
\end{itemize}

\ul{Lab assistant} \hfill Spring 2019 - Spring 2021 
\begin{itemize}
\item Lab assistant for MATH 340: Intro to Scientific Computing at Western Carolina University for three semesters.
\item Taught \LaTeX{}, Excel, Mathematica, \texttt{MATLAB}, and \texttt{R} to students from diverse majors, including mathematics, computer science, engineering, biology, and chemistry.
\item Developed hands-on activities for students to complete in and out of class to either facilitate understanding of course topics, or explore applications.
\item Assisted students in debugging code during hands-on class time.
\end{itemize}

\ul{Course tutor} \hfill Spring 2017 - Spring 2019
\begin{itemize}
\item Tutored several courses at Western Carolina University's student tutoring center, including introductory biology, organic chemistry, genetics, evolutionary biology, immunology, and microscopy.
\item Worked one-on-one with students to reinforce course content, including working with non-traditional students.
\item Adapted course information to the individual learning styles of a diverse client body.
\item Led group tutoring and review sessions where I was responsible for assisting several students at once with course material.
\end{itemize}

\vspace{0.2in}
\textbf{Other research:}

\setlist{nolistsep}
\begin{itemize}[noitemsep]
\item \ul{Lab technician}: Coan Lab and cell culture facility, Western Carolina University. Spring 2019 -- Fall 2020. Maintained human cell cultures and ensured lab was OSHA compliant.
\item \ul{OEIS (On-line Encyclopedia of Integer Sequences) Contributions}: All of these sequences can be viewed at \url{https://oeis.org}.
	\setlist{nolistsep}
	\begin{itemize}[noitemsep]
		\item Author of sequence \href{https://oeis.org/A319302}{\ul{A319302}}.
		\item Author of sequence \href{https://oeis.org/A309092}{\ul{A309092}}.
		\item Wrote Python code and generated a b-file for sequence \href{https://oeis.org/A110529}{\ul{A110529}.}
	\end{itemize}
\item \ul{Population Biology of Infectious Diseases REU participant}. Worked with Andreas Handel at the University of Georgia in Summer 2019. Research resulted in McKay et al. publication in Open Forum Infectious Diseases.
\item \underline{Math-Biology REU participant}. Worked with Louis-Marie Bobay at the University of North Carolina at Greensboro in Summer 2018.
\item \ul{Senior thesis.} Worked with Heather Coan at Western Carolina University as part of obtaining my B.S. degree; this research resulted in a thesis available upon request.
\end{itemize}

\vspace{0.2in}
\textbf{Skills:}

\setlist{nolistsep}
\begin{itemize}[noitemsep]
%\item Responsible Conduct in Research (RCR) certified (CITI Program).
%\item CRLA certified Level 1 Tutor.
\item Programming: \ul{\texttt{R}}, SAS, Python, MATLAB, Git and GitHub, bash.
\item Software: Mathematica (Wolfram language), Tableau.
\item Presentation: \LaTeX{}, Markdown (R-Markdown), HTML/CSS.
\end{itemize}

\end{document}