\documentclass[10pt]{moderncv}

\usepackage{xcolor}

% moderncv themes
\moderncvstyle{banking}
\moderncvcolor{black}
%\renewcommand{\familydefault}{\sfdefault}         % to set the default font; use '\sfdefault' for the default sans serif font, '\rmdefault' for the default roman one, or any tex font name

\usepackage{tgpagella}
\usepackage[T1]{fontenc}
\usepackage{soul}
%\usepackage{hyperref}
\usepackage[utf8]{inputenc}
\usepackage[scale=0.75, margin = 1in]{geometry}
%\setlength{\hintscolumnwidth}{3cm}                % if you want to change the width of the column with the dates
%\setlength{\makecvtitlenamewidth}{10cm}           % for the 'classic' style, if you want to force the width allocated to your name and avoid line breaks. be careful though, the length is normally calculated to avoid any overlap with your personal info; use this at your own typographical risks...

% personal data
%\name{W. Zane}{Billings}
%\address{2347 Old NC 27 Hwy.}{Mount Holly, NC 28120}{USA}
%\phone[Mobile]{+1~(980)~241~7815}                   % optional, remove / comment the line if not wanted; the optional "type" of the phone can be "mobile" (default), "fixed" or "fax"
%\phone[fixed]{+2~(345)~678~901}
%\phone[fax]{+3~(456)~789~012}
%\email{wzbillings1@catamount.wcu.edu}                               % optional, remove / comment the line if not wanted
%\homepage{www.johndoe.com}                         % optional, remove / comment the line if not wanted
%\social[linkedin]{john.doe}                        % optional, remove / comment the line if not wanted
%\social[twitter]{jdoe}                             % optional, remove / comment the line if not wanted
%\social[github]{jdoe}                              % optional, remove / comment the line if not wanted
%\extrainfo{additional information}                 % optional, remove / comment the line if not wanted
%\photo[64pt][0.4pt]{picture}                       % optional, remove / comment the line if not wanted; '64pt' is the height the picture must be resized to, 0.4pt is the thickness of the frame around it (put it to 0pt for no frame) and 'picture' is the name of the picture file
%\quote{2347 Old NC 27 Hwy \\ Mount Holly, NC 28120 \\ (980) 241-7815 \\ wzbillings1@catamount.wcu.edu}                                 % optional, remove / comment the line if not wanted

% bibliography adjustements (only useful if you make citations in your resume, or print a list of publications using BibTeX)
%   to show numerical labels in the bibliography (default is to show no labels)
\makeatletter\renewcommand*{\bibliographyitemlabel}{\@biblabel{\arabic{enumiv}}}\makeatother
%   to redefine the bibliography heading string ("Publications")
%\renewcommand{\refname}{Articles}

% bibliography with mutiple entries
%\usepackage{multibib}
%\newcites{book,misc}{{Books},{Others}}
%----------------------------------------------------------------------------------
%            content
%----------------------------------------------------------------------------------
\begin{document}
%\begin{CJK*}{UTF8}{gbsn}                          % to typeset your resume in Chinese using CJK
%-----       resume       ---------------------------------------------------------
\begin{center}
{\Huge \textbf{Curriculum Vitae}} \\
\vspace{0.25in}
{\Large W. Zane Billings}
\end{center}

\vspace{-0.25in}

\section{Contact Information}
\textbf{Email:} \texttt{\href{mailto:wzbillings1@catamount.wcu.edu}{wzbillings1@catamount.wcu.edu}} \\
\textbf{Phone:} (980) 241-7815 \\
\textbf{Mailing address:} 2347 Old NC 27 Highway, Mount Holly, NC 28120-9758 \\
\textbf{LinkedIn:} \texttt{\href{https://www.linkedin.com/in/zane-b/}{zane-b}} \\
\textbf{GitHub:} \texttt{\href{https://github.com/wz-billings}{wz-billings}} \\
\textbf{OEIS:} \texttt{\href{https://oeis.org/A319302}{W. Zane Billings}}

\section{Education}
\cventry{2016--2020}{Mathematics and Biology, B.S.}{Western Carolina University}{Cullowhee, NC}{4.0 GPA}{
\begin{itemize}
    \item Concentrations: Applied mathematics, molecular biology
    \item Minor: Chemistry
\end{itemize}
}

\textit{Honors and Awards:}
\begin{itemize} \small{
    \item Chancellor's List, every semester
    \item WCU Distinguished Achievement Scholarship (2016 - 2020)
    \item Several other scholarship awards from Biology, Mathematics, and the Honors College.
    \item Math and Computer Science Department Ambassador, Fall 2018 onward
    \item COMAP Mathematical Contest in Modeling 2019: Meritorious Winnter (Problem A)}
\end{itemize}
%\cventry{2012--2016}{Valedictorian out of 426}{East Gaston High School}{Mount Holly, NC}{}{}

% \textit{Organizations}
% \begin{itemize}
%     \item Sigma Alpha Pi, the National Society for Leadership and Success
%     \item Alpha Lambda Delta national honor society
% \end{itemize}

%\cventry{year--year}{Degree}{Institution}{City}{\textit{Grade}}{Description}

% \section{Master thesis}
% \cvitem{title}{\emph{Title}}
% \cvitem{supervisors}{Supervisors}
% \cvitem{description}{Short thesis abstract}

\section{Employment}
\cventry{Fall 2018--Present}{Lab manager, researcher}{Coan Lab at Western Carolina University}{Cullowhee, NC}{}{
\begin{itemize}
    \item Supervised by Dr. Heather Coan at WCU.
    \item Researched the autophagy pathway, focused on stress-induced autophagy in human cells.
    \item Utilized several techniques from mammalian cell culture and fluorescence microscopy.
    \item Ensured the lab environment, including the cell culture facility, was tidy and complied with BSL-2 and OSHA saftey standards.
    \item Prepped cell cultures and solutions for other lab workers and assisted with use of lab technology such as the fluorescence microscope and culture room.
    \item Worked with the Advanced Techniques in Microscopy Laboratory, mainly assisting with data analysis protocols. 
\end{itemize}
}
\cventry{Spring 2019 -- present}{Mathematics lab assistant}{Mathematics and Computer Science Department, WCU}{Cullowhee NC}{}{
\begin{itemize}
    \item Worked as a lab assistant for the hands-on, programming based course MATH 340: Introduction to Scientific Computing. This course is designed as a first introduction to programming and scientific computing, and is primarily taken by math, computer science, and engineering students.
    \item Assisted several students with \LaTeX{}, \texttt{MATLAB}, \texttt{R}, and Mathematica coding, as well as Excel spreadsheet development.
    \item Developed educational activities to strengthen coding skills for in-class use.
\end{itemize}}
%%%SUMMER 2019 REU%%%
\cventry{Summer 2019}{Researcher; REU participant}{Population Biology of Infectious Diseases REU}{Athens, GA}{Handel Research Group}{
\begin{itemize}
    \item Participated in the 2019 Summer NSF-funded REU program at the University of Georgia, Athens.
    \item Wrote \texttt{R} code to perform a variety of tasks, including cleaning and joining data, summarizing and visualizing data, and constructing models.
    \item Analyzed cross-sectional data from a study performed at UGA's Student Health Clinic, in order to analyze the clinical revelance of qPCR data to influenza prognosis and care.
    \item Communicated results of data analysis through markdown, intermediate progress presentations, and a final poster presentation.
    \item Worked with Dr. Handel to prepare walkthroughs and solutions to several learning modules for the \href{https://github.com/ahgroup/DSAIDE}{DSAIDE} \texttt{R} package.
\end{itemize}}

\cventry{Summer 2018}{Researcher; REU participant}{Math-Bio REU at the University of North Carolina, Greensboro}{Greensboro, NC}{Bobay Research Group}{
\begin{itemize}
    \item Utilized methods from genomics to analyze large DNA sequence datasets.
    \item Visualized data for the project using R.
    \item Contributed to mathematical models of convergent mutations between DNA strands.
    \item Assisted in the design of Python simulations to verify findings.
\end{itemize}}
\cventry{Spring 2017--Spring 2019}{Course Tutor}{Writing and Learning Commons at WCU}{Cullowhee, NC}{}{
\begin{itemize}
    \item Tutored peers in material from introductory biology, organic chemistry and genetics. As of Spring 2019, I am tutoring Immunology, Advanced Techniques in Microscopy, and Evolutionary Biology.
    \item Identified strategies for working with students who had different learning techniques.
    \item Communicated with professors regarding material students did and did not know, and questions which came up commonly during tutoring.
\end{itemize} }
\cventry{July 2014-- August 2016}{Proofreader}{New River Engineering, PLLC}{Mount Holly, NC}{}{I proofread emails, project proposals, and technical reports to provide grammatical and stylistic corrections.}

% \section{Languages}
% \cvitemwithcomment{Language 1}{Skill level}{Comment}
% \cvitemwithcomment{Language 2}{Skill level}{Comment}
% \cvitemwithcomment{Language 3}{Skill level}{Comment}

\section{Research Experience}
\cventry{Spring 2016--Present}{Mentor: Heather Coan}{Cell Biology}{Western Carolina University}{}{I conducted independent research on autophagic flux. My research utilized several tools from molecular biology and microscopy in order to elucidate stress-induced autophagic flux in human cells. I maintained bacterial cultures and extracted plasmids, maintained human cell cultures, transfected plasmids into human cells, and stressed cells before visualization using widefield fluoresence microscopy. After visualization, I was involved in image processing and designed analyses for the data.}
\cventry{Summer 2019}{Mentor: Andreas Handel}{Epidemiology and Biostatistics}{University of Georgia, Athens}{}{As part of the Population Biology of Infectious Diseases REU, funded by the NSF and NIH, I worked with the Handel research group. My research included the development of software packages in the \texttt{R} language for epidemiology education, and analysis of flu data collected at the UGA student health center.}
\cventry{Summer 2018}{Mentor: Louis-Marie Bobay}{Computational Biology}{University of North Carolina, Greensboro}{}{As part of the Math-Biology REU site, I worked on a team modeling the rate of convergent mutation between bacterial genomes. In order to predict rates of homologous recombination, we constructed a probabilistic model of recombination and designed and ran several simulations to verify.}
\cventry{Fall 2017--Spring 2018}{Mentor: William Kwochka}{Organic Chemistry}{Western Carolina University}{}{I conducted independent research in organic chemistry. The lab group's work focused on characterizing the nature of the ``dative bond'' between Lewis acid-base complexes. I synthesized several derivatives of an organic boron-containing compound and complexed several of these bonds. Additionally, I characterized these compounds using spectroscopic methods.}
\cventry{Summer 2016}{Mentor: Jeremy Hyman}{Behavioral Ecology}{Western Carolina University}{}{As part of a two-week program (SURP) prior to my first semester at WCU, I assisted Dr. Hyman and a senior undergraduate student with her thesis work on the behavior of song sparrows. I mainly participated in the field component of the research, assisting with bird song playback experiments as well as catching a bird.}

\section{Skills}
\cvdoubleitem{Lab techniques}{Aseptic technique, mammalian cell culture and transfection, fluorescence microscopy, PCR, ELISA, Western blot, CITI Program responsible conduct in research certification.}{Programming}{Proficient with \texttt{R} (including Base and Tidyverse), \LaTeX, and Markdown, intermediate proficiency with Python, familiar with Git and CSS.}  %\textbf{Interpersonal:} ITTPC Level I tutor certification, .}
% \cvdoubleitem{category 2}{XXX, YYY, ZZZ}{category 5}{XXX, YYY, ZZZ}
% \cvdoubleitem{category 3}{XXX, YYY, ZZZ}{category 6}{XXX, YYY, ZZZ}

\section{Relevant Coursework}
\cvdoubleitem{Biology}{Immunology, Advanced Techniques in Microscopy, Protein Systems and Bioinformatics, Cell Biology, Evolutionary Biology, Origin of Species}{Mathematics}{Differential Equations, Linear Algebra, Statistical Methods (I--Intro \& II--Time Series and Linear Regression), Scientific Computing, Linear Optimization, Introductory Probability Theory, Mathematical Modeling}
%\cvdoubleitem{Computer Science}{Intro to Python Programming, Data Storytelling with Tableau}{Other}{Homeland Security}

%\section{Presentations}
%\subsection{Peer Reviewed}
%\cvlistitem{Billings WZ, Youker RT, Coan H. Visualization of autophagic flux in HEK293 cells via dual-reporter LC3 plasmid transfection. Molecules in the Mountains. 2018 Apr 12. Western Carolina University, NC.}
%\subsection{Not Peer Reviewed}
%\cvlistitem{Billings WZ, Schatz KM, Yang J. Estimating bacterial recombination rates. 2018 UNCG REU Symposium. 2018 July 20. University of North Carolina, Greensboro, NC.}
%\cvlistitem{Billings WZ, Schatz KM, Yang J. Modeling rates of homologous recombination in bacteria. 2018 MATH REU Conference. 2018 July 9. Clemson University, SC.}
%\cvlistitem{Billings WZ, Thompson E. Cloning and sequencing of GAPC in \textit{Carex appalachia}. Cell and Molecular Biology Presentations. 2018 May 1. Western Carolina University, NC.}
%\cvlistitem{Billings WZ, Schatz KM, Yang J. Modeling recombination. 2018 Math Colloquim Series, Western Carolina University, NC.}

% \section{Miscellaneous}
% \cvlistitem{Author of sequence \texttt{\href{https://oeis.org/A319302}{A319302}} on the OEIS.}

% \section{Publications}
% \cvlistitem{Item 1}
% \cvlistitem{Item 2}
% \cvlistitem{Item 3}

% \section{References}
% \begin{cvcolumns}
%   \cvcolumn{Category 1}{\begin{itemize}\item Person 1\item Person 2\item Person 3\end{itemize}}
%   \cvcolumn{Category 2}{Amongst others:\begin{itemize}\item Person 1, and\item Person 2\end{itemize}(more upon request)}
%   \cvcolumn[0.5]{All the rest \& some more}{\textit{That} person, and \textbf{those} also (all available upon request).}
% \end{cvcolumns}

% Publications from a BibTeX file without multibib
%  for numerical labels: \renewcommand{\bibliographyitemlabel}{\@biblabel{\arabic{enumiv}}}% CONSIDER MERGING WITH PREAMBLE PART
%  to redefine the heading string ("Publications"): \renewcommand{\refname}{Articles}
% \nocite{*}
% \bibliographystyle{plain}
% \bibliography{publications}                        % 'publications' is the name of a BibTeX file

% Publications from a BibTeX file using the multibib package
%\section{Publications}
%\nocitebook{book1,book2}
%\bibliographystylebook{plain}
%\bibliographybook{publications}                   % 'publications' is the name of a BibTeX file
%\nocitemisc{misc1,misc2,misc3}
%\bibliographystylemisc{plain}
%\bibliographymisc{publications}                   % 'publications' is the name of a BibTeX file

\clearpage
% %-----       letter       ---------------------------------------------------------
% % recipient data
% \recipient{Company Recruitment team}{Company, Inc.\\123 somestreet\\some city}
% \date{January 01, 1984}
% \opening{Dear Sir or Madam,}
% \closing{Yours faithfully,}
% \enclosure[Attached]{curriculum vit\ae{}}          % use an optional argument to use a string other than "Enclosure", or redefine \enclname
% \makelettertitle

% Lorem ipsum dolor sit amet, consectetur adipiscing elit. Duis ullamcorper neque sit amet lectus facilisis sed luctus nisl iaculis. Vivamus at neque arcu, sed tempor quam. Curabitur pharetra tincidunt tincidunt. Morbi volutpat feugiat mauris, quis tempor neque vehicula volutpat. Duis tristique justo vel massa fermentum accumsan. Mauris ante elit, feugiat vestibulum tempor eget, eleifend ac ipsum. Donec scelerisque lobortis ipsum eu vestibulum. Pellentesque vel massa at felis accumsan rhoncus.

% Suspendisse commodo, massa eu congue tincidunt, elit mauris pellentesque orci, cursus tempor odio nisl euismod augue. Aliquam adipiscing nibh ut odio sodales et pulvinar tortor laoreet. Mauris a accumsan ligula. Class aptent taciti sociosqu ad litora torquent per conubia nostra, per inceptos himenaeos. Suspendisse vulputate sem vehicula ipsum varius nec tempus dui dapibus. Phasellus et est urna, ut auctor erat. Sed tincidunt odio id odio aliquam mattis. Donec sapien nulla, feugiat eget adipiscing sit amet, lacinia ut dolor. Phasellus tincidunt, leo a fringilla consectetur, felis diam aliquam urna, vitae aliquet lectus orci nec velit. Vivamus dapibus varius blandit.

% Duis sit amet magna ante, at sodales diam. Aenean consectetur porta risus et sagittis. Ut interdum, enim varius pellentesque tincidunt, magna libero sodales tortor, ut fermentum nunc metus a ante. Vivamus odio leo, tincidunt eu luctus ut, sollicitudin sit amet metus. Nunc sed orci lectus. Ut sodales magna sed velit volutpat sit amet pulvinar diam venenatis.

% Albert Einstein discovered that $e=mc^2$ in 1905.

% \[ e=\lim_{n \to \infty} \left(1+\frac{1}{n}\right)^n \]

% \makeletterclosing
\end{document}